\chapter*{Acknowledgements}

First of all, I would like to express my thanks to my dissertation thesis supervisors, 
Ing.\,Viktor Pu\v{s},\,Ph.D. and doc.\,Ing.\,Hana Kub\'atov\'a,\,CSc., for their support, valuable comments and guidance. 
They have been a constant source of encouragement and insight during my research and helped me with numerous problems and professional advancements.

Special thanks go to the staff of the Liberouter project, funded by CESNET, and the \Department{} of the Czech Technical University in Prague, 
who maintained a pleasant and flexible working environment for my research. 
I would like to express special thanks to the management of both institutions for providing of the funding for my research.
My research has been partially supported 
%skolni granty
by the Czech Technical University in Prague, grants No. SGS14/102/OHK3/042/14, No. SGS14/105/OHK3/1T/18, No. SGS15/122/OHK3/1T/18,
%granty cestnetu pod ministerstvem skolstvi
by the Ministry of Education, Youth, and Sports of the Czech Republic under research programs CESNET Large Infrastructure project No. LM2010005,
CESNET E-infrastructure project No. LM2015042,
%EU projekty
by the European Union in the context of the BEBA project (Grant Agreement: 644122)
%TACR projekty
and by the projects TA03010561, TH01010229 funded by the Technology Agency of the Czech Republic.

I would like to express thanks to my colleagues from the Liberouter group, namely Ing.\,Luk\'a\v{s} Kekely, Ing.\,Jan Ko\v{r}enek,\,Ph.D., 
Ing.\,Martin \v{Z}\'adn\'ik,\,Ph.D., Ing. Tom\'a\v{s} \v{C}ejka and others, 
for their valuable comments and motivation in my research.

My greatest thanks go to Petra and my family members for their infinite patience, care, love and support. 
Finally, I would like to greatly thank to my father MVDr.\,Zden\v{e}k Ben\'a\v{c}ek for his love, patience and amazing childhood because 
he suddenly died after the long disease on 3 December 2015 . 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original content                                                            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%First of all, I would like to express my gratitude to my dissertation thesis
%supervisor, Dr. R\'obert~L\'orencz. He~has been a constant source of encouragement and insight during my research and helped me with numerous problems and professional advancements.  
%
%I would like to thank to Dr. \dots, and Prof. \dots for giving me \dots
%
%Special thanks go to the staff of the \Department{}, who maintained a pleasant and flexible environment for my research. I would like to express special thanks to the department management for providing most of the funding for my research. 
%% The following is important, as it refers to ``Vyzkumny zamer''.
%My research has also been partially supported 
%by the Ministry of Education, Youth, and Sport of the Czech Republic under research program MSM~6840770014, 
%by the Czech Science Foundation as project No. 201/06/1039, 
%by the Grant Agency of the Czech Technical University in Prague, grant No. SGS \dots, and
%by the \dots
%I would like to express thanks to my colleagues from \dots group, namely Mr. \dots, Ms. \dots, Dr. \dots, and others, for their valuable comments and proofreading.
%
%Finally, my greatest thanks go to my family members, for their infinite patience and care \dots
