\section{Conclusion and Contributions}
\subsection*{Conclusion and Contributions}
\begin{frame}
    \frametitle{Conclusion and Contributions}
    \begin{itemize}
        \fitem \textbf{My research is focused on mapping of abstract description to VHDL model of high-speed network device}
        \fitem I provided the following:
        %
        \begin{enumerate}
            \fitem Modular architecture of high-speed network device (\textbf{100\,Gbps} and beyond)
            \fitem Process of mapping from \textbf{P4 language} (introduced in 2013) to the architecture of high-speed network device
            \fitem Tool --- for verification of architecture and mapping process
            \fitem Overview of usage of High Level Synthesis (C/C++) in high throughput designs. 
            Results of this research were used in other research projects. 
        \end{enumerate}
        %
        \fitem The quality of generated code is comparable to hand-written one
        \begin{itemize}
            \fitem More resources are the cost for flexibility
        \end{itemize}
        \fitem The result of this research was verified against real network test devices
    \end{itemize}
\end{frame}

\subsection*{Publications and Evaluation Activities}
\begin{frame}[allowframebreaks]
    \frametitle{Publications and Evaluation Activities}
    %
    {
    % Use the small font in all publications
    \footnotesize
    \textbf{\underline{Reviewed Publications of the Author Relevant to the Thesis}}
    \begin{itemize}
        \fitem[$\rightarrow$] \textbf{[FCCM16]} P. Ben\'{a}\v{c}ek, V. Pu\v{s} and H. Kub\'{a}tov\'{a}.
        \textit{P4-to-VHDL: Automatic Generation of 100Gbps Packet Parsers}. IEEE 24\textsuperscript{th} Annual International Symposium on Field-Programmable Custom Computing Machines (FCCM2016), Washington D.C., USA, 2016.
        %
        \fitem[$\rightarrow$] \textbf{[H2RC15]} P. Ben\'{a}\v{c}ek, V. Pu\v{s} and H. Kub\'{a}tov\'{a}. \textit{Automatic Generation of 100 Gbps Packet Parsers from P4 Description}.
        First International Workshop on Heterogeneous High-performance Reconfigurable Computing, Austin, TX, USA, 2015.
        %
        \fitem[$\rightarrow$] \textbf{[DSD14]} P. Ben\'{a}\v{c}ek, H. Kub\'{a}tov\'{a} and V. Pu\v{s}. \textit{Architecture of Effective High-Speed Network Stream Merger}.
        Digital System Design (DSD), 17\textsuperscript{th} Euromicro Conference on Digital System Design, pp. 459--464, Verona, Italy, 2014.
        %
        \fitem[$\rightarrow$] \textbf{[FPGA14]} P. Ben{\'a}{\v{c}}ek and V. Pu{\v{s}}.
        \textit{Application specific processor with high-level synthesized instructions}.
        ACM/SIGDA international symposium on Field-Programmable Gate Arrays, pp. 246--246, Monterey, CA, USA,
        2014.
        %
        \fitem[$\rightarrow$] \textbf{[ANCS14]} P. Ben\'{a}\v{c}ek, T. \v{C}ejka, H. Kub\'{a}tov\'{a} and R. Bla\v{z}ek.
        \textit{Change-Point Detection Method on 100 Gb/s Ethernet Interface}.
        ACM/IEEE Symposium on Architectures for Networking and Communications Systems, Marina del Rey, CA, USA,
        2014.
        \smallskip \\ The paper has been cited in:
        \begin{itemize}
            \footnotesize
            \fitem Nakamura, Kohei, Ami Hayashi, and Hiroki Matsutani. \textit{An FPGA-Based Low-Latency Network Processing for Spark Streaming}. Proceedings of the Workshop on Real-Time and Stream Analytics in Big Data (IEEE BigData 2016 Workshop), 2016.
        \end{itemize}
        %
        \fitem[$\rightarrow$] \textbf{[MEMICS14]} P. Ben\'{a}\v{c}ek, T. \v{C}ejka, H. Kub\'{a}tov\'{a}, L. Kekely and R. Bla\v{z}ek.
        \textit{FPGA Accelerated Change-Point Detection Method for 100 Gb/s Networks}.
        Doctoral Workshop on Mathematical and Engineering Methods in Computer Science, Tel\v{c}, Czech Republic,
        2014.
        %
        \fitem[$\rightarrow$] \textbf{[H2RC16]} P. Ben\'{a}\v{c}ek, V. Pu\v{s} and P. Ka\v{s}tovsk\'y.
        \textit{P4-to-FPGA: High Performance Reconfigurable Networking (poster)}.
        Second International Workshop on Heterogeneous High-performance Reconfigurable Computing, Salt Lake City, UT, USA,
        2016.
        %        
        \fitem[$\rightarrow$] \textbf{[P4ST16]} P. Ben{\'a}{\v{c}}ek and V. Pu{\v{s}}.
        \textit{P4-to-VHDL: Generating High Speed Network Devices (poster)}. 
        P4 Workshop, Stanford, California, USA, 
        2016.
        %
        \fitem[$\rightarrow$] \textbf{[FPL13]} L. Kekely, V. Pu\v{s}, P. Ben{\'a}\v{c}ek and J. Ko\v{r}enek.
        textit{Trade-offs and progressive adoption of FPGA acceleration in network traffic monitoring}.
        Field Programmable Logic and Applications (FPL), 24\textsuperscript{th} International Conference, pp. 1--4, Munich, Germany,
        2014.
        \smallskip \\ \smallskip The paper has been cited in:
        \begin{itemize}
            \footnotesize
            \item D. Grochol, L. Sekanina, M. \v{Z}\'{a}dn\'{i}k, J. Ko\v{r}enek. \textit{Evolutionary circuit design for fast FPGA-based classification of network application protocols}. 
            Applied Soft Computing, Volume 38, January 2016, pp. 933-941.
            \item L. Tang, J. Yan, Z. Sun, T. Li, M. Zhang. \textit{Towards high-performance packet processing on commodity multi-cores: current issues and future directions}.
            Research Paper Special Focus On Future Internet Architecture And Protocol Science China Information Sciences, December 2015, Volume 58, Issue 12, pp. 1-16.
        \end{itemize}
    \end{itemize}
    %
    \textbf{\underline{Submitted Publications}}
    \begin{itemize}
        \fitem[$\rightarrow$] \textbf{[MICPRO16]} P. Ben\'{a}\v{c}ek, H. Kub\'{a}tov\'{a} and V. Pu\v{s}.
        \textit{P4-to-VHDL: Automatic Generation of High-Speed Input and Output Network Blocks}.
        Microprocessors and Microsystems, Elsevier Journal, 2016.
    \end{itemize}
    %
    \textbf{\underline{Evaluation Activities}}
    \begin{itemize}
      \fitem[$\rightarrow$] Review of article for the \textit{Journal of Parallel and Distributed Computing}. Article in journal, ISSN 0743-7315, 2016.
      %
      \fitem[$\rightarrow$] Conference Programme Committee member in the \textit{Track on Reconfigurable Computing for Networks and Communications}. International Conference on Reconfigurable Computing and FPGAs (ReConFig'2016), Cancun, Mexico, 2016.
    \end{itemize}
    %
    \textbf{\underline{P4 Popularization}}
    \begin{itemize}
        \fitem[$\rightarrow$] \textbf{[ROOT16]} P. Ben{\'a}{\v{c}}ek and V. Pu{\v{s}} 
        \textit{The P4 Language as the Future of SDN (CZ)}. 
        root.cz (part 1 and part 2), 2016.
        %
        \fitem[$\rightarrow$] \textbf{[P4CES16]} P. Ben{\'a}{\v{c}}ek and V. Pu{\v{s}} 
        \textit{The P4 Language as the Future of SDN (CZ)}. 
        CESNET blog, 2016 
       
     \end{itemize}
    } 
\end{frame}
